Model-theoretic aspects of relativised cylindric set algebras

### 2020-10-15 problem-9.4/Text.tex
cylindric background

@@

Let $\alpha$ be an ordinal. Let $U^{\alpha}$ be the set of all functions mapping $\alpha$ to a non-empty set $U$. We denote $x(i) = x_i$ for
$x \in U^{\alpha}$ and $i < \alpha$.

@@

  \begin{enumerate}
    \item A subset of $U^{\alpha}$ is an $\alpha$-ry relation on $U$. For $i, j < \alpha$, the $i,j$-diagonal $D_{ij}$ is the set of all
    elements of $U$ such that $y_i = y_j$. If $i < \alpha$ and $X$ is an $\alpha$-ry relation on $U$, then
    the $i$-th cylindrification $C_i X$ is the set of all elements of $U$ that agree with some element of $X$ on each coordinate except the
    $i$-th one. To be more precise,
    $C_i X = \{ y \in U^{\alpha} \: | \: \exists x \in X \forall i < \alpha \: (i \neq j \Rightarrow y_j = x_j)\}$.
    \item A cylindic set algebra of dimension $\alpha$ is an algebra consisting of a set $S$ of $\alpha$-ry relation on some base set $U$
    with the constants and operations $0 = \emptyset$, $1 = U^{\alpha}$, $\cap$, $-$, the diagonal elements $\{ D_{ij} \}_{i, j < \alpha}$,
    the cylindrifications $\{ C \}_{i < \alpha}$. A generalised cylindric set algebra of dimension $\alpha$ is a subdirect of
    cylindric algebras that have dimension $\alpha$
    \item A cylindric algebra of dimension $\alpha$ is an algebra $\mathcal{C} = \langle \mathcal{B}, \{ c_i \}_{i < \alpha}, \{ d_{ij} \}_{i, j < \alpha} \rangle$ such that
    \begin{itemize}
      \item $\mathcal{B}$ is a Boolean algebra, for each $i, j < \alpha$ $c_i$ is an operator and $d_{ij} \in \mathcal{B}$
      \item For each $i < \alpha$, $a \leq c_i a$, $c_i (a \land c_i b) = c_i a \land c_i b$ and $d_{ii} = 1$
      \item For every $i, j < \alpha$, $c_i c_j a = c_j c_i a$
      \item If $k \neq i, j < \alpha$, then $d_{ij} = c_k (d_{ij} \land d_{jk})$
      \item If $i \neq j$, then $c_i (d_{ij} \land a) \land c_i (d_{ij} \land - a) = 0$
    \end{itemize}
    ${\bf CA}_{\alpha}$ is the class of all cylindric algebras of dimension $\alpha$
    \item An $\alpha$-dimensional cylindric algebra $C$ is representable, if it is isomorphic to a generalised cylindric set algebra
    of dimension $\alpha$. Such is isomorphism is a representation of $C$.
    ${\bf RCA}_{\alpha}$ is the class of all representable cylindric algebras that have dimension $\alpha$. In particular, we are interested in the case when $\alpha = \omega$.
  \end{enumerate}
\end{defin}

>>>>

\section{Intro}
...
It is known that the equational theory of ${\bf RCA}_{\omega}$ for $\alpha \leq \omega$ is decidable \cite{nemeti1996fine}.
...

@@

Let $\alpha$ be an ordinal. Let $\prescript{\alpha}{}U$ be the set of all functions mapping $\alpha$ to a non-empty set $U$. We denote $x(i) = x_i$ for
$x \in \prescript{\alpha}{}U$ and $i < \alpha$.

@@

  \begin{enumerate}
    \item A subset of $\prescript{\alpha}{}U$ is an $\alpha$-ry relation on $U$. For $i, j < \alpha$, the $i,j$-diagonal $D_{ij}$ is the set of all
    elements of $U$ such that $y_i = y_j$.

    If $i < \alpha$ and $X$ is an $\alpha$-ry relation on $U$, then
    the $i$-th cylindrification $C_i X$ is the set of all elements of $U$ that agree with some element of $X$ on each coordinate except the
    $i$-th one. To be more precise,
    $C_i X = \{ y \in \prescript{\alpha}{}U \: | \: \exists x \in X \forall i < \alpha \: (i \neq j \Rightarrow y_j = x_j)\}$.
    \item A cylindic set algebra of dimension $\alpha$ is an algebra consisting of a set $S$ of $\alpha$-ry relation on some base set $U$
    with the constants and operations $0 = \emptyset$, $1 = \prescript{\alpha}{}U$, $\cap$, $-$, the diagonal elements $\{ D_{ij} \}_{i, j < \alpha}$,
    the cylindrifications $\{ C \}_{i < \alpha}$.

    A generalised cylindric set algebra of dimension $\alpha$ is a subdirect of
    cylindric algebras that have dimension $\alpha$
    \item A cylindric algebra of dimension $\alpha$ is an algebra $\mathcal{C} = \langle \mathcal{B}, \{ c_i \}_{i < \alpha}, \{ d_{ij} \}_{i, j < \alpha} \rangle$ such that
    \begin{itemize}
      \item $\mathcal{B}$ is a Boolean algebra, for each $i, j < \alpha$ $c_i$ is an operator and $d_{ij} \in \mathcal{B}$
      \item For each $i < \alpha$, $a \leq c_i a$, $c_i (a \land c_i b) = c_i a \land c_i b$ and $d_{ii} = 1$
      \item For every $i, j < \alpha$, $c_i c_j a = c_j c_i a$
      \item If $k \neq i, j < \alpha$, then $d_{ij} = c_k (d_{ij} \land d_{jk})$
      \item If $i \neq j$, then $c_i (d_{ij} \land a) \land c_i (d_{ij} \land - a) = 0$
    \end{itemize}
    ${\bf CA}_{\alpha}$ is the class of all cylindric algebras of dimension $\alpha$
    \item An $\alpha$-dimensional cylindric algebra $C$ is representable, if it is isomorphic to a generalised cylindric set algebra
    of dimension $\alpha$. Such is isomorphism is a representation of $C$.

    ${\bf RCA}_{\alpha}$ is the class of all representable cylindric algebras that have dimension $\alpha$. In particular, we are interested in the case when $\alpha = \omega$.
  \end{enumerate}
\end{defin}

It is well-known that ${\bf RCA}_{\alpha}$ is a variety, ${\bf RCA}_{\alpha}$ ($\alpha \leq 2$) is finitely axiomatisable and ${\bf RCA}_{\alpha}$ ($2 < \alpha < \omega$) has no finite axiomatisation, see \cite{Henkin1988-HENCAP-4}.

Let $\mathcal{A} \in {\bf C}_{\omega}$, then $\mathcal{A}$ has a \emph{complete representation}, if this representation preserves all existing suprema.

Let us discuss the connection between representability and canonical extensions.

\begin{defin}
  neat embeddable
\end{defin}
